Rough Draft

### 2017-11-15 Article submission/roughdraft.tex
edited results

\begin{itemize}
  \item The average tag ``score'' for all of a question's tags. Score is defined as the proportion of times a tag appears in all of the data. Questions without tags were assigned an average tag score of 0. 
  \item The average number of characters in each question's tags. 
  \item The number of characters in the question's text. 
  \item The number of characters in the user-defined device name. 
  \item The ratio of the number of line breaks to the number of characters in the question's text.
\end{itemize}

@@

Survival was defined as the event that a question does not receive an answer beyond a certain time, t. Estimates of survival probability were generated with the Kaplan-Meier method (cite). This method adjusts to the presence of right-censored, or unanswered questions. Estimates factor in the number of questions that have not been answered on each ordered interval of complete answer times. The estimates of survival probablity are the products of all probabilities up to that interval's time (fix this explanation). From these estimates, survival curves were constructed to examine the survival experience of questions. Mean, median and other percentiles of survival times were also generated.

As the probability distribution for answer times was unknown, a nonparametric Cox proportional hazards model was developed to predict survival probability (Cox models are not based on an assumption of the shape of the underlying probability distribution). To build the model, five-fold cross-validation was used. The full data was split into five training and five test sets. Each training set contained 6,208 questions, and each test set contained 1,552 questions. Univariate analysis, performed on one of the training sets, was used to identify variables to potentially include in the final Cox proportional hazards model. Predictors were entered into separate Cox models and the strength of association between those predictors and answer times were assessed. Those with partial likelihood ratio test p-values of less than 0.01 were included in the full model.

In each fold of cross-validation, the full model, with variables found to be signficant in univariate analysis, was built on one of the training sets and used to generate predicted hazard ratios on the corresponding test sets. To assess prediction performance, the predicted hazard ratios were entered into separate Cox models as the single quantitative predictor with answer times as the survival time. The resulting estimated hazard ratio, R-square statistic, partial likelihood ratio and p-value were assessed as indicators of the full model's performance \citep{Chen}. Signficant statistics would indicate high predictive accuracy. Concordance statistics and Somers' Dxy were also assessed to measure the model's predictive discrimination. Concordance is defined as the probability that for any two randomly chosen questions, the question with the shorter survival time also has the higher predicted hazard. Concordance statistics close to 1 indicate high discriminative ability, while statistics close to 0.5 indicate discordance, or random predictions. Somers' Dxy is the difference between the model's concordance statistic and discordance (0.5) \citep{Harrell2015}. These metrics were computed for each training and test set. The averages of metrics across test sets were evaluated. The final model was selected based on AIC statistics and signficance of prediction metrics, as well as how consistent those metrics were across training and test sets. The final model was then fit to the full data and the same metrics were computed and compared.

Plots of Martingale residuals, the differences between observed number of answers received by each question and the expected number of answers expereinced by each question under the model, were evaluated to assess functional form of each continuous predictor. Deviance residuals, transformed Martingale residuals with a mean of 0 and approximately normal distribution, were assessed to identify questions poorly predicted by the model. Score residuals, a measure of the approximate change in parameter estimates that would occur if a question were removed from the sample, were assessed to check for questions that highly effect parameter estimates.

As the data analyzed was fairly large, restricted cubic splines were applied to all continuous predictors \citep{Harrell2015}. Splines of five knots were initially fit to each. The optimal number of knots for each predictor was determined based on the model AIC statistic. A higher number of knots were assigned to predictors hypothesized to be more signficant, those with lower model p-values.

Correlations between scaled Schoenfeld residuals, the differences between observed and expected predictor values for each question that received an answer, and a function of time were examined to assess the proportional hazards assumption that underlies a Cox proportional hazards model. Proportional hazards assumes that the effect of predictors on hazard does not depend on time. Significant correlations would indicate that a predictor has violated this assumption.

@@

  Of 7,760 questions, 63.8\% received an answer by the download date. Figure a shows the distribution of answer times for all questions, grouped by whether or not the question received an answer. Figure B shows the Kaplan-Meier curve of survival probability for all questions in the data. The Kaplan-Meier estimated mean survival time, or the average time until a question received its first answer was 775.75 hours, or 32.32 days. The median survival time, the time at which 50\% of the questions in the data received an answer was 9.16 hours. Table 1 provides additional percentiles of survival time.

Predictors with p-values less than 0.01 in univariate analysis are shown in table b. The univariate model for the average frequency of a question's tags displayed an extrememly high hazard coefficient (33.8). To address this, a square root transformation was used on the variable, bringing the hazard coefficient to 4.2. Average performance metrics for the full model and its predictions for test and training sets, found in table c, were considerably low. However, metrics did not change substantially from training to test set, indicating that the model does not overfit. A spline of five knots was fit to the number of characters in the user-defined device name. Splines of four knots were fit to the number of characters in a question's text, average number of characters in a question's tags, and the ratio of number of line breaks to the number of characters in a question's text. Results of cross-validation for the model including the splines are in table d. As refitting the model without insignificant predictors did not effect predictive performance, all variables were included. The final model, with all variables described above including splines, was fit to the full data.

Score and deviance residuals of the final model identified outliers and highly influential questions. However, because refitting the model without those questions resulted in worse predictive accuracy, all questions were left in the data. Assessing the proportional hazards assumption indicated that several levels of the device category predictor were in violation. But as stratifying on this predictor substantially decreased predictive accuracy, the variable was left as is. Statistics and parameter coefficients of the final model are in table c.

>>>>

\begin{itemize}
  \item The average tag ``score'' for all of a question's tags. A tag score is defined as the proportion of times a tag appears in all of the data. Questions without tags were assigned an average tag score of 0. 
  \item The average number of characters in each question's tags. 
  \item The number of characters in the question's text. 
  \item The number of characters in the user-defined device name. 
  \item The ratio of the number of line breaks to the number of characters in the question's text.
\end{itemize}

@@

Survival was defined as the event that a question did not receive an answer beyond a certain time, t. Estimates of survival probability were generated with the Kaplan-Meier method (cite), which adjusts to the presence of right-censored, or unanswered questions. This method factors in the number of questions that have not been answered on each ordered interval of complete answer times. Estimates of survival probablity are the products of all probabilities up to that interval's time (redo this). From these estimates, survival curves were constructed to examine the survival experience of questions, and mean, median and other percentiles of survival times were also generated.

As the probability distribution for answer times was unknown, a nonparametric Cox proportional hazards model was developed to predict survival probability (Cox models are not based on an assumption of the shape of the underlying probability distribution (cite)). To build the model, five-fold cross-validation was used. The full data was split into five training and five test sets. Each training set contained 6,208 questions, and each test set contained 1,552 questions. Univariate analysis, performed on one of the training sets, was used to identify variables to potentially include in the final Cox proportional hazards model. Distributions of continuous variables constructed on one of the training sets, were assessed and transformations were applied. Each categorical and continuous predictor, both with and without transformations, were entered into separate Cox models and strength of association with answer times were assessed. Those with partial likelihood ratio test p-values of less than 0.01 were included in the full model for cross-validation.

In each fold of cross-validation, the full model, with variables found to be signficant in univariate analysis, was built on one of the training sets and used to generate predicted hazard ratios on the corresponding test sets. To assess prediction performance, the predicted hazard ratios were entered into separate Cox models as the single quantitative predictor with answer times as the survival time. The resulting estimated hazard ratio, R-square statistic, partial likelihood ratio and p-value were assessed as indicators of the full model's performance \citep{Chen}. Signficant statistics would indicate high predictive accuracy. Concordance statistics and Somers' Dxy were also assessed to measure the model's predictive discrimination. Concordance is defined as the probability that for any two randomly chosen questions, the question with the shorter survival time also has the higher predicted hazard. Concordance statistics close to 1 indicate high discriminative ability, while statistics close to 0.5 indicate discordance, or random predictions. Somers' Dxy is the difference between the model's concordance statistic and discordance, 0.5 \citep{Harrell2015}. These metrics were computed for each training and test set. The averages of metrics across test sets were evaluated. The final model was selected based on AIC statistics and the signficance of prediction metrics, as well as how consistent those metrics were across training and test sets. The final model was then fit to the full data and the same metrics were computed and compared.

Plots of Martingale residuals, the differences between observed number of answers received by each question and the expected number of answers expererienced by each question under the model, were evaluated to assess functional form of each continuous predictor. Deviance residuals, which are transformed Martingale residuals with a mean of 0 and an approximately normal distribution, were assessed to identify questions poorly predicted by the model. Score residuals, a measure of the approximate change in parameter estimates that would occur if a question were removed from the sample, were assessed to check for questions that highly effect parameter estimates.

Restricted cubic splines were applied to all continuous predictors \citep{Harrell2015}. Splines of five knots were initially fit to each. A higher number of knots were assigned to predictors hypothesized to be more signficant, those with lower model p-values. The optimal number of knots for each predictor was determined based on the model AIC statistic.

Correlations between scaled Schoenfeld residuals, the differences between observed and expected predictor values for questions that received answers, and a function of time, were examined to assess the proportional hazards assumption that underlies a Cox model. Proportional hazards assumes that the effect of predictors on hazard does not depend on time. Significant correlations indicate that a predictor has violated this assumption.

@@

  Of 7,760 questions, 4,651 (63.8\%) received an answer by the download date. The shortest answer time was 0.01 hours. The longest was 2159.02 hrs (89.96 days). Figure a shows the distribution of answer times for all questions, grouped by whether or not the question received an answer. Figure B shows the Kaplan-Meier curve of survival probability for all questions in the data. The curve indicates that 150 hours after a question has been posted, survival probability coasts at around 0.35 and never reaches 0, indicating that if a question does not receive an answer within the first 100 hours after it has been posted, the likelihood of it receiving an answer in the future is low. The Kaplan-Meier estimated mean survival time, or the average time until a question received its first answer was 775.75 hours, or 32.32 days. The median survival time, the time at which 50\% of the questions in the data received an answer, was 9.16 hours. Table 1 provides additional percentiles of survival time.

As the distributions of continuous predictors were extremely right-skewed, the following transformations were applied:

Log transformation
\begin{itemize}
  \item number of characters in a question's text
\end{itemize}

Square root transformations
\begin{itemize}
  \item The average score of a question's tags.
  \item The average number of characters in a question's tags.
  \item The number of characters in a question's user-defined device name.
  \item The ratio of the number of line breaks to the number of characters in the question's text.
\end{itemize}

Predictors with p-values less than 0.01 are shown in Table b. All transformed continuous and categorical predictors were entered into the full model for cross-validation. Average performance metrics for test and training sets, found in table c, were considerably low. However, metrics did not change substantially from training to test sets, indicating that the model does not overfit. The following restricted cubic splines were applied continuous variables:

4 knots
\begin{itemize}
  \item number of characters in the user-defined device name
\end{itemize}

3 knots
\begin{itemize}
  \item number of characters in a question's text
  \item square root of the average number of characters in a question's tags
  \item ratio of number of line breaks to the number of characters in a question's text
\end{itemize}

Results of cross-validation for the model including splines are in table d. As refitting the model without insignificant predictors and reperforming cross-validation did not change predictive accuracy, all variables were included. The final model, with all variables described above including splines, was fit to the full data.

Score and deviance residuals of the final model identified outliers and highly influential questions. However, because refitting the model without those questions resulted in worse predictive accuracy, all questions were left in the data. Assessing the proportional hazards assumption indicated that several predictors were in violation. P-values for the correlation between predictors schoenfeld residuals and time are shown in table e. But as stratifying on this predictor substantially decreased predictive accuracy, the variable was left as is. Statistics and parameter coefficients of the final model are in table c. Metrics for the final model's performance on the full data, though considerably low, are not different from the metrics computed in cross-validation.
